IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
lio

\subsection{Haskell}
\label{sec:real:hs}
Our work borrows many ideas from the Haskell coarse-grained IFC
system LIO~\cite{lio, stefan:addressing-covert}.
%
LIO relies on Haskell's strong type system and monadic encoding of
side-effecting computations to achieve isolation and define the IFC
sub-language.
%
Specifically LIO provides the \verb|LIO| monad as a way of restricting
(almost all) side-effects; this monad also keeps track of a current
label which is, in turn, used by functions such as |getLabel| to
define the IFC core.
%
In the context of our framework, LIO can be understood as follows: the
\emph{pure subset} of Haskell is the target language, while the
monadic subset of Haskell in the \verb|LIO| monad is the IFC language.

Indeed, by rephrasing LIO in terms of our framework, we simplified
LIO's treatment of exceptions, which have since been integrated in the
code-base.
%
we addressed a limitation in LIO.

>>>>

\subsection{Haskell}
\label{sec:real:hs}
Our work borrows many ideas from the Haskell coarse-grained IFC
system LIO~\cite{lio, stefan:addressing-covert}.
%
LIO relies on Haskell's strong type system and monadic encoding of
side-effecting computations to achieve isolation and define the IFC
sub-language.
%
Specifically LIO provides the \verb|LIO| monad as a way of restricting
(almost all) side-effects; this monad also keeps track of a current
label which is, in turn, used by trusted code when defining core IFC
functions, such as |getLabel|.
%
In the context of our framework, LIO can be understood as follows: the
\emph{pure subset} of Haskell is the target language, while the
monadic subset of Haskell, operating in the \verb|LIO| monad, is the
IFC language.

Indeed, by rephrasing LIO in terms of our framework, we simplified
LIO's treatment of exceptions.
%
LIO originally associated labels with exceptions, in a
similar style to fine-grained
systems~\cite{stefan:2012:arxiv-flexible, Breeze}.
%
In particular, the label of an exception was set to the current label
at the time of the throw, and used by a custom catch construct to
raise the current label, thereby preventing leaks due exceptional
control flows.
%
In addition to being overly complex, the interaction of exceptions
with clearance (which sets an upper bound on the current label, see
Section~\ref{sec:extensions:clearance}) was incorrect: the clearance
was restored to the clearance at point of the catch (a consequence of
defining \verb|LIO| using a State monad).
%
Moreover, pure exceptions (e.g., divide by zero) always percolated to
trusted code, effectively allowing for denial of service attacks.
%
By using isolated tasks, and thus treating the current label (and
clearance) as global, the underlying Haskell exception system can be
used directly: exceptional control flow does not affect IFC.
